Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-07-10 paper.tex
fjkldsjf

This work recommends introducing two major changes to the standard G-PTM-D workflow: a spectral calibration, and a replacement of the standard searches with custom mass-window type searches.
In order to clearly show the advantage of each proposed change, they are initially discussed in isolation, and then the following section shows the combined effect on the overall G-PTM-D performance.

>>>>

This work presents four major changes to the previously published G-PTM-D workflow:
a spectral calibration;
a replacement of the wide parent mass tolerance search with a custom multi-notch search for PTM discovery;
replacement of the final traditional narrow mass search with a limited multi-notch search that permits identification of incorrectly deconvoluted precursor masses;
and lastly, addition of capacity for identification of multiple cofragmented peptides from a single MS/MS scan.
To clarify the advantage of each change, they are first discussed separately, followed by an analysis of their combined effect upon overall G-PTM-D performance.
